Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-04 Final-Draft.Rmd
changes fixing finaldata

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day))
day_initial<- as.Date("03/14/2020")
day_final<- as.Date("03/21/2020")

@@

View(Finaldata)
```

>>>>

Finaldata <- Finaldata %>% mutate(Day= as.Date(Day, tryFormats = "%m/%d/%Y"))

day_initial<- as.Date("03/14/2020",tryFormats = "%m/%d/%Y")
day_final<- as.Date("03/21/2020",tryFormats = "%m/%d/%Y")

@@
